Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2013-01-06 docs/tex/experiments.tex
Added utils pdb fetch command and redefined experiments

@@

@@

\subsubsection{Tied SCOP - Multistate proteins}

>>>>

We have the following sources of information from the various databases :

\begin{itemize}
\item pdb - pfam map
\item pdb - scop - pdb list map
\item pdb - sec structure map
\item pdb - seq map
\item pdb - pdb structure 
\item pfam - pdb 
\item pfam - uniprot (alignments)
\end{itemize}

@@

\subsubsection{Tied SCOP Zif268-Trimer}
\label{exp:tied_scop_multistate}
For multistate design we will look try to design for two states Zif268(zic-finger like) and a trimeric coiled coil. Specifically we will consider the structures of hemaglutinin(13-44) pdb id 1HTM and Zif268 zinc-finger DNA complex(pdb id: 1AAY). 1HTM belongs to the PF00509 family which has 232 structures. 1AAY belongs to PF00096 family which has 19 structures. These sets are expanded by considering the SCOP family that they belong to. 1AAY belongs to the Zif268 domain which has 14 structures and the zinc finger family which has 70 structures. 1HTM belongs to influenza hemagluttinin family and domain which have 39 structures both. In order to train the hmm, one can learn the transition and emission probabilities of the region under consideration, the whole protein. One can also choose to learn these weights from just the PFAM or just the scop data or both combined. We will explore each of these cases.

\subsubsection{Untied SCOP-PFAM Zif268-Trimer}
\label{exp:untied_scop_zif}

@@
